Typed Functional Genetic Programming

### 2013-06-23 tex/thesis.tex
[tex] ...

This step consists of two sub steps\footnote{TODO : Technically it is done in a little  
bit different fashion which is equivalent.}:
\begin{itemize} 
	\item Selection of \textit{parents} for individuals of the next population based on the fitness.
	      The bigger fitness of an individual of the current population is, 
	      the better chance of success being selected as parent it has.  
	\item Application of genetic operators (such as \textit{crossover}, 
	      \textit{reproduction} and \textit{mutation}) 
		  on parent individuals producing new individuals of the next population.  
\end{itemize}	  
This transformation is repeatedly applied for a predefined number of steps (which is called 
number of \textit{generations}) or until some predefined criterion is met.	
\\\\
\Lets now look on GP at more detail. Here is pseudocode for GP algorithm:

>>>>

This step consists of two sub steps\footnote{TODO : Technically it is done in a little  
bit different fashion which is equivalent.}:
\begin{itemize} 
	\item Selection of \textit{parents} for individuals of the next population based on the fitness.
	      The bigger fitness of an individual of the current population is, 
	      the better chance of success being selected as parent it has.  
	\item Application of genetic operators (such as \textit{crossover}, 
	      \textit{reproduction} and \textit{mutation}) 
		  on parent individuals producing new individuals of the next population.  
\end{itemize}	  
This transformation is repeatedly applied for a predefined number of steps (which is called 
number of \textit{generations}) or until some predefined criterion is met.	
\\\\
\Lets now look on GP at more detail.

\subsection{Program trees}

In GP programs are represented as expressions. \Lets define expression inductively:

\begin{itemize}
	\item Constant or variable symbol $s$ is expression.
	\item Let there be a function with symbol $f$ which has $n$ arguments. 
	      And let there be expressions $e_{1}, ..., e_{n}$. 
	      Then ( $f$ $e_{1}$ ... $e_{n}$ ) is expression.   
\end{itemize}

There is straightforward tree representation corresponding to these two cases:

\begin{itemize}
	\item One node tree $s$.
    \item \Tree
			[.$f$	
		 		\text{$t_{1}$}
		 		\text{...}
		 		\text{$t_{n}$} ]\\\\
		 Where $t_{1}, ..., t_{n}$ are trees corresponding to expressions $e_{1}, ..., e_{n}$.	   
\end{itemize}

Computer program with inputs $x_{1}, ..., x_{n}$ is realized as expression in which 
may occur variables $x_{1}, ..., x_{n}$.

\subsection{Building blocks}

Set of building blocks consists of two sets.

\begin{itemize}
	\item Terminal set $T$ : Set of symbols used as leaf nodes of program trees.
	\item Function set $F$ : Set of symbols used as internal nodes of program trees.
\end{itemize}

Therefore $building$ $blocks = T \cup F$.

\subsection{GP algorithm in pseudocode}

Here is pseudocode for GP algorithm:
